Parallel-in-time Methods with Machine Learning - Report

### 2020-03-24 report/MSc-report.tex
Update on Overleaf.

>>>>

Some dynamical systems have an inherently finite spatial domain and there are only so many subdomains this space can be decomposed into. The number of these subdomains limits the level of parallelism achievable using traditional parallel numerical methods. Parallel-in-time methods address this by solving the differential equation describing the system in parallel along the time axis unlocking potentially higher levels of parallelism. The most notable parallel-in-time method, the Parareal algorithm, does this by using an expensive fine operator and a computationally cheap coarse operator
